Neuroecon Poster Figures

### 2017-10-02 code/NeuroeconPoster.Rmd
added outline for poster both in code and in ppt

>>>>

Lit review figure

```{r}

```

Bootstrapped reliabilities figure mirroring lit review figure
(most likely excludes DDM)

```{r}

```

Histogram of point estimates comparing distributions of survey vs. task measures

```{r}

```

Stats comparing reliabilities of surveys vs tasks

```{r}

```

Table for survey reliabilities by survey name

```{r}

```

Stats checking if item number makes a difference for reliability estimates for surveys

```{r}

```

Table for task reliabilities by task name

```{r}

```

Stats checking if item number makes a difference for reliability estimates for tasks

```{r}

```

Table for task reliabilities by cognitive construct

```{r}

```

Histogram of DDM vs. RT and accuracy measures

```{r}

```

Statistics comparing average reliabilities for DDM vs raw measures

```{r}

```

Note on metric for retest reliabilities
Scatter plots showing relationships between ICC, Pearson and Spearman

```{r}

```
